---
title: "wk2-workshop"
author: "TW"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
```

```{r}
df = readRDS("data/wk2_stocks.rds")
str(df)
```

## Qn1. Find the following statistics about the S&P returns.

The cumulative returns of the S&P index during this period is `r round(sum(df$SPY_returns) *100, 2)`%.
The average daily returns of the S&P index during this period is `r round(mean(df$SPY_returns) *100, 2)`%.
The standard deviation of the daily returns of the S&P index during this period is `r round(sd(df$SPY_returns) *100, 2)`%.

## Qn2. Create a plot that shows the prices of S&P in this period.
```{r}
ggplot(data = df, aes(x = date, y = SPY_prices)) +
  geom_line()
```

## Qn3. Create a plot that shows the total yearly returns of S&P from 2001 to 2023.
```{r}
df1 = df %>%
  mutate(year = year(date)) %>% 
  group_by(year) %>% 
  filter(year %in% (2001:2023)) %>% 
  summarise(yearly_return = sum(SPY_returns)*100)

ggplot(df1, aes(x = year, y = yearly_return)) +
  geom_col()
```